Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-08-25 manuscripts/manuscript.Rmd
updated runs

theme_set(theme_tufte() + theme(axis.line = element_line()))
```

@@

fig3_df <- as.data.frame(subset(dt, replicate=='rep_17'))
fig3_df <- fig3_df[c("time", "fishstock", "alternate", "harvest", "harvest_alt", "penalty_fn")]
fig3_df <- melt(fig3_df, id = c("time", "penalty_fn"))
fig3_df <- data.frame(fig3_df, baseline = fig3_df$variable)
variable_map <- c(fishstock = "fish_stock", alternate = "fish_stock", harvest = "harvest", harvest_alt = "harvest")
baseline_map <- c(fishstock = "penalty", alternate = "no_penalty", harvest = "penalty", harvest_alt = "no_penalty")
fig3_df$variable <- variable_map[fig3_df$variable]
fig3_df$baseline <- baseline_map[fig3_df$baseline]

harvest_fig3 <- subset(fig3_df, variable=="harvest")
fishstock_fig3 <- subset(fig3_df, variable=="fish_stock")

@@

ggplot(harvest_fig3, aes(time, value, col=baseline)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("Reed solution", "With penalty"), name="")

write.csv(harvest_fig3, "components/data/figure3.csv")
```

Figure 3 illustrates how the different forms of adjustment cost can impact
the optimal harvest policy. Corresponding stock sizes can be seen in the
supplement.  Each panel is generated against the same sequence of random
shocks so that they can be compared directly.  The harvest policy chosen
shows a systematic deviations from the penalty free optimum, depending on
the nature of the cost.  In each case, the optimal solution without any
adjustment cost is shown in against the policy induced by optimization
under the given adjustment penalty (equivalent to a `r 100*reduction`%
reduction in maximum expected NPV) is overlaid in blue.

<!-- NOTE FIXME make this consistent! -->

@@

<!-- to include cross.correlation, drop subset call and facet_wrap by variable. But shows no pattern-->

@@

```{r Figure_5, fig.cap="Distribution of profits from fishing and costs paid to adjustment.  Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.  In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png")}

@@

who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
table1 <- arrange(error_df[who], reduction) 
names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
table1_long$reduction <- as.factor(table1_long$reduction)
table1_long <- subset(table1_long, reduction != "0.3")
ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, ncol=2) + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Penalty function")
write.csv(table1_long, "components/data/figure6.csv")
```

@@

```{r Figure_7, fig.cap="Mismatches. X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty. Blue bars show the net present value of that scenario.  Compare to red bars, which show the consequence of using a policy that ignores costs all together in the same scenario (i.e. costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.  All values are scaled to a fraction of the adjustment free net present value.  Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g. a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.", dev=c("pdf", "svg", "png"), fig.width=7}
who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
table2 <- arrange(mismatches_df[who], reduction) 
names(table2) = c("penalty.fn", "ignoring", "mismatched", "reduction")
table2_long <- melt(table2, id = c('penalty.fn', 'reduction'))
table2_long$reduction <- as.factor(table2_long$reduction)

ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y") +
  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
  xlab("Penalty function")
write.csv(table2_long, "components/data/figure7.csv")
```

@@

labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[1-3]))), 
            harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
            fishstock = substitute(paste("Stock dynamics under under ", paste(Pi[1-3]))), 
            alternate = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")
ex <- dt %>% 
  filter(replicate %in% paste0("rep_", 10:20) & penalty_fn == "L1" & time < 20) %>%
  select(time, fishstock, harvest, alternate, harvest_alt) %>%
  gather(variable, stock, -time, -replicate)

ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=labels, name="") +  
  facet_wrap(~replicate)

@@

>>>>

theme_set(theme_tufte(base_size=12) + theme(axis.line = element_line()))
```

@@

@@

dt3 <- dt %>% 
  filter(replicate=="rep_17" & time < 20) %>%
  select(time, harvest, harvest_alt, penalty_fn) %>%
  gather(variable, value, -time, -penalty_fn)

ggplot(dt3, aes(time, value, col=variable, lty=variable)) +
  geom_line(lwd=1) +
  facet_grid(penalty_fn~., labeller = labeller) + 
  labs(x="time", y="stock size", title = "Example Harvest Dynamics")  +
  scale_color_discrete(labels=c("With Penalty", "Reed Solution"), name="") +
  scale_linetype_discrete(labels=c("With Penalty", "Reed Solution"), name="")

write.csv(dt3, "components/data/figure3.csv")
```

Figure 3 illustrates how the different forms of adjustment cost can impact
the optimal harvest policy. Corresponding stock sizes can be seen in the
supplement.  Each panel is generated against the same sequence of 
environmental variability so that they can be compared directly.  The harvest policy chosen
shows a systematic deviations from the penalty free optimum, depending on
the nature of the cost.  In each case, the optimal solution without any
adjustment cost is shown with the policy induced by optimization
under the given adjustment penalty (equivalent to a `r 100*reduction`%
reduction in maximum expected NPV) overlaid in blue.

@@

@@

```{r}
fig5_caption <- paste("Distribution of profits from fishing and costs paid to adjustment, under linear costs (Pi[1]). (Alternate penalties can be found in the supplementary materials)  Distributions are shown when managing a system in which the adjustment costs present compared to the same costs and profits of managing the system using a Reed model, which ignores adjustment costs, and thus tends to pay higher fees for adjustment.  In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).")
```

```{r Figure_5, fig.cap=fig5_caption, fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png")}

fig5_dat <- hist_dat %>% 
  filter(penalty_fn=="L1") %>%
  select(-penalty_fn) %>%
  unite(dist, Assumption, variable, sep = " : ")

ggplot(fig5_dat) + 
  geom_density(aes(value, fill=dist, color=dist), alpha=0.8)

@@

who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
table1 <- arrange(error_df[who], reduction) 
names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
table1_long$reduction <- as.factor(table1_long$reduction)
table1_long <- subset(table1_long, reduction != "0.3")

ggplot(filter(table1_long, reduction == 0.25),
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, ncol=2) + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Penalty function")
write.csv(table1_long, "components/data/figure6.csv")
```

@@

```{r Figure_7, fig.cap="Mismatches. X axis labels indicate the model used to derive the policy, followed by the model used to simulate the penalty. Blue bars show the net present value of that scenario.  Compare to red bars, which show the consequence of using a policy that ignores costs all together in the same scenario (i.e. costs as indicated by second code), rather than assuming the policy indicated by the first code in the pair.  All values are scaled to a fraction of the adjustment free net present value.", dev=c("pdf", "svg", "png"), fig.width=7}
who <- c("penalty_fn", "ignore_fraction", "mismatched_fraction", "reduction")
table2 <- arrange(mismatches_df[who], reduction) 
names(table2) = c("penalty.fn", "ignoring", "mismatched", "reduction")
table2_long <- melt(table2, id = c('penalty.fn', 'reduction'))
table2_long$reduction <- as.factor(table2_long$reduction)

ggplot(filter(table2_long, reduction==0.25), 
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y") +
  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
  xlab("Penalty function")
write.csv(table2_long, "components/data/figure7.csv")
```

@@

labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[1-3]))), 
            harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")),
            fishstock = substitute(paste("Stock dynamics under under ", paste(Pi[1-3]))), 
            alternate = substitute(paste("Stock under ", paste(Pi[0]), " (Reed)")))
labeller <- function(variable,value){
if (variable=='penalty_fn') {
    return(relabel[paste(value)])
  } else {
    return(value)
  }
}

ex <- dt %>% 
  filter(replicate %in% paste0("rep_", 16:20) & time < 20) %>%
  select(time, fishstock, harvest, alternate, harvest_alt, replicate, penalty_fn) %>%
  gather(variable, stock, -time, -replicate, -penalty_fn)

ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=labels, name="") +  
  facet_grid(replicate ~ penalty_fn, labeller=labeller)

@@

```{r Figure_S3, fig.cap="Distribution of profits from fishing and costs paid to adjustment.  Distributions are shown when managing a system in which the adjustment costs present are determined by the model indicated, and compared to the same costs and profits of managing the same system using a Reed model, which ignores adjustment costs, and thus tends to pay much higher fees for adjustment.  In contrast, the difference in profit after accounting for costs is only marginally less than the value derived by managing the population to optimize profits when ignoring adjustment costs (Reed model).", fig.width=8, fig.height=6, dependson="histogram-calc", dev=c("pdf", "svg", "png")}

```{r Figure_S4, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost-free adjustment optimum, NPV0.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs.", dev=c("pdf", "svg", "png"), fig.width=7}

ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, ncol=2) + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Penalty function")
write.csv(table1_long, "components/data/figure6.csv")
```

```{r Figure_S5, fig.cap="Effect of varying severity of adjustment costs on mismatches. Successive panels show increasing reduction of the net present value by increasing penalty coefficients: e.g. a policy in the first panel would lose only 10% (panel A) of its net present value to adjustment costs if it had the correct form of those costs, as determined by the choice of penalty coefficient.  Plots structured as in figure 7, which corresponds to the fourth panel", dev=c("pdf", "svg", "png"), fig.width=7}
ggplot(table2_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  facet_wrap(~reduction, scales="free_y") +
  scale_x_discrete(labels = c('L1_L2' = substitute(paste(Pi[1],"_", Pi[2])), 
                              'L2_L1' =  substitute(paste(Pi[2],"_", Pi[1])),
                              'L1_fixed' = substitute(paste(Pi[1],"_", Pi[3])), 
                              'fixed_L1' =  substitute(paste(Pi[3],"_", Pi[1])),
                              'fixed_L2' = substitute(paste(Pi[3],"_", Pi[2])), 
                              'L2_fixed' =  substitute(paste(Pi[2],"_", Pi[3])))) + 
  xlab("Penalty function")
write.csv(table2_long, "components/data/figure7.csv")
```
